Fermi and eROSITA bubbles: a proof of concept study

### 2021-12-19 paper.tex
update

  \begin{subequations}
    \label{conservative-form}
    \begin{align}
     &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
     &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=\
     -\rho\partial_{i}\Phi,\label{M evolution}\\
     &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
     &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=\
     -p_{\text{cr}} \partial_{j} U^{j},\label{D evolution}
    \end{align}
  \end{subequations}

@@

  The set of equations is closed by using the Taub-Mathews equation of state (\citealt{Taub}; \citealt{TM_EOS})\
  that approximates the exact EoS \citep{Synge} for ultra-relativistically\
  hot gases coexisting with non-relativistically cold gases.

@@

  \subsection{The Galactic Model}

  As a proof-of-concept study, we approximate conventionally axisymmetric potential of Milky Way\
  by a plane-parallel potential that is symmetric about the mid-plane $z=0$\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

  The plane-parallel potential is fixed throughout our simulations and given by

  \begin{equation}
    \Phi_{\text{total}} = \Phi_{\text{bulge}} + \Phi_{\text{halo}},
  \end{equation}

  where

  \begin{equation}
    \Phi_{\text{bulge}}=\
    2\sigma^2_{\text{bulge}}\
    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right)
  \end{equation}

  is the potential of a isothermal slab mainly contributed by stars within the Galactic plane.

  $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
  is a plane-parallel dark logarithmic halo potential.

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  the steady-state gaseous density distribution in a total potential, $\Phi_{\text{total}}$,\
  can be written as
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right] & \text{, otherwise.}
     \end{cases}
  \end{equation}

  where $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the mass density\
  of the bulge and atmosphere on the $z=0$ plane.

  All parameters are listed in \Cref{table-parameters}, excpet for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the pressure equilibrium on the interfaces ($|z|=z_{0}$) between disk and atmosphere.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrr@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                           & Description                       & Value                                & Reference                         \\ \midrule
{\bf Disk}                          &                                   &                                      &                                   \\
$z_{0}$                             & Scale height of disk              & 100 pc                               & \citep{peak-ism-density}          \\
$T_{\text{\text{disk}}}$            & Temperature of disk               & $10^{3}$ K                           & \citep{peak-ism-density}          \\
$\rho_{\text{disk}}^{\text{peak}}$  & Peak mass density of disk         & $10^{-23}$ g/cm$^{3}$                & \citep{peak-ism-density}          \\ \hline
{\bf Atmosphere}                    &                                   &                                      &                                   \\
$T_{\text{\text{atmp}}}$            & Temperature of atmosphere         & $10^{6}$ K                           & \citep{temperature-MW}            \\ \hline
{\bf Potential \& halo}             &                                   &                                      &                                   \\
$\sigma_{\text{bulge}}$             & Velocity dispersion of bulge      & 100 km/s                             & \citep{velocity-dispersion-MW}    \\
$\rho_{\text{bulge}}^{\text{peak}}$ & Peak average density of bulge     & $4\times 10^{-24}$ g/cm$^{3}$        &                                   \\
$v_{\text{halo}}$                   &                                   & 131.5 km/s                           & \citep{Johnston1995}              \\
$d_{\text{h}}$                      & Core radius                       & 12 kpc                               & \citep{Johnston1995}              \\ \midrule
\end{tabular}
\end{table*}

>>>>

  \begin{subequations}
    \label{governing-eq}
    \begin{align}
     &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
     &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=\
     -\rho\partial_{i}\Phi,\label{M evolution}\\
     &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
     &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=\
     -p_{\text{cr}} \partial_{j} U^{j},\label{D evolution}
    \end{align}
  \end{subequations}

@@

  The set of \Cref{governing-eq} is closed by using the Taub-Mathews equation of state (\citealt{Taub}; \citealt{TM_EOS})\
  that approximates the exact EoS \citep{Synge} for ultra-relativistically\
  hot gases coexisting with non-relativistically cold gases.

@@

  \subsection{The Galactic Model}
  As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
  by an external plane-parallel potential that is symmetric about the mid-plane $z=0$\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

  The plane-parallel potential is fixed throughout our simulations and given by
  \begin{equation}
    \Phi_{\text{total}}(z) = \Phi_{\text{bulge}}(z) + \Phi_{\text{halo}}(z),
  \end{equation}
  where
  \begin{equation}
    \Phi_{\text{bulge}}(z)=\
    2\sigma^2_{\text{bulge}}\
    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right)
  \end{equation}
  is the potential of an isothermal slab mainly contributed by stars around the Galactic plane, and\
  $\Phi_{\text{halo}}(z)=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
  is a plane-parallel dark logarithmic halo potential.

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  the steady-state gaseous density distribution of disk and atmosphere\
  confined in the total potential, $\Phi_{\text{total}}$,\
  can be written as
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
     \end{cases}
  \end{equation}
  where $m_{\text{p}}$ is a proton mass,\
  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the bulge and atmosphere on the mid-plane $z=0$.

  All parameters are listed in \Cref{table-parameters}, excpet for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium\
  on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrr@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                             & Description                   & Value                          & Reference                       \\ \midrule
{\bf Disk }\citep{peak-ism-density}                   &                               &                                &                                 \\
$z_{0}$                                               & Scale height of disk          & 100 pc                         &                                 \\
$T_{\text{\text{disk}}}$                              & Temperature of disk           & $10^{3}$ K                     &                                 \\
$\rho_{\text{disk}}^{\text{peak}}$                    & Peak mass density of disk     & $10^{-23}$ g/cm$^{3}$          &                                 \\ \hline
{\bf Atmosphere }\citep{temperature-MW}               &                               &                                &                                 \\
$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere     & $10^{6}$ K                     &                                 \\ \hline
{\bf Static stellar potential }                       &                               &                                &                                 \\
$\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge  & 100 km/s                       & \citep{velocity-dispersion-MW}  \\
$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$  &                                 \\ \hline
{\bf Static dark halo potential }\citep{Johnston1995} &                               &                                &                                 \\
$v_{\text{halo}}$                                     &                               & 131.5 km/s                     &                                 \\
$d_{\text{h}}$                                        & Core radius                   & 12 kpc                         &                                 \\ \midrule
\end{tabular}
\end{table*}
